A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-19 tex/body.tex
more

To simplify the presentation, we make a few assumptions about
$\Sig$.
First, all codatatypes in $\Codata$ are corecursive. This is reasonable
because noncorecursive codatatypes can be seen as nonrecursive
datatypes.
Second, all types $\tau \in \Nondata$ have infinite cardinality.
This is not very restrictive, because in principle each interpreted type in
$\Nondata$ having finite cardinality~$n$
can be replaced by a %n enumeration
datatype with $n$~nullary constructors
\cite{barrett-et-al-2007}.
As for uninterpreted types, since the constraints in $\Ec$
are ground, they cannot entail an upper
bound on the cardinality of any such type, so it is safe to consider them infinite.

@@

{\looseness=-1
A derivation rule can be applied to $\Ec$ if %all
the %specified
preconditions are met.
The conclusion either describes equalities to be added to $\Ec$
or is $\bot$. % (contradiction).
% (in which case we call an application of it \emph{nonterminal})
% (in which case we call an application of it \emph{terminal}).
One rule has multiple conclusions, % separated by $\ror$,
denoting branching.
%
An application of a rule is \emph{redundant} if one branch in the
conclusion is an assignment to $\Ec$ that leaves it unchanged.
A \emph{derivation tree} is a %finite
tree whose nodes are finite sets of
equalities and where child nodes are obtained by a nonredundant application of a
derivation rule to the parent. A derivation tree is \emph{closed} if all of
its leaf nodes are $\bot$. A node is \emph{saturated} if no nonredundant
instance of a rule can be applied to it.

>>>>

To simplify the presentation, we make a few assumptions about
$\Sig$.
First, all codatatypes in $\Codata$ are corecursive. This is reasonable
because noncorecursive codatatypes can be seen as nonrecursive
datatypes.
Second, all types $\tau \in \Nondata$ have infinite cardinality.
This is not very restrictive, because in principle each interpreted type in
$\Nondata$ having finite cardinality~$n$
can be replaced by a %n enumeration
datatype with $n$~nullary constructors
\cite{barrett-et-al-2007}.
As for uninterpreted types, since the constraints in $\Ec$
are ground, they cannot entail an upper
bound on the cardinality of any such type, so it is safe to consider these types infinite.

@@

{\looseness=-1
A derivation rule can be applied to $\Ec$ if %all
the %specified
preconditions are met.
The conclusion either specifies equalities to be added to $\Ec$
or is $\bot$. % (contradiction).
% (in which case we call an application of it \emph{nonterminal})
% (in which case we call an application of it \emph{terminal}).
One rule has multiple conclusions, % separated by $\ror$,
denoting branching.
%
An application of a rule is \emph{redundant} if one branch in the
conclusion is an assignment to $\Ec$ that leaves it unchanged.
A \emph{derivation tree} is a %finite
tree whose nodes are finite sets of
equalities and where child nodes are obtained by a nonredundant application of a
derivation rule to the parent. A derivation tree is \emph{closed} if all of
its leaf nodes are $\bot$. A node is \emph{saturated} if no nonredundant
instance of a rule can be applied to it.
